UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-19 paper/paper.tex
updates

Total number of machines: 12583
0.5 and 0.5,0.25 = 10595 = 84.2\% = heavy
rest = 1988 = 15.8\% = medium

@@

>>>>

Measurement period = 29 days
Total number of machines: 12583
0.5 and 0.5,0.25 = 10595 = 84.2\% = heavy
rest = 1988 = 15.8\% = medium

@@

\begin{center}
    \begin{tabular}{| l | l | l | l | l | l | l | l |}
    \hline
    Total cost & Cost for heavy & Cost for medium & Total Uptime & Total distance & CPU & Memory & Tasks \\ \hline
    \$8 177 048 & \$7 479 648 & \$697 400 & 8 705 743h & +3 215 231 & 15972217.38 & 30676363.36 & 1234716525 \\ \hline
    \end{tabular}
\end{center}

Cost per task = \$8 177 048 / 1234716525 = \$0.00662261161525
cost per hour = \$8 177 048 / 8 705 743 = 0.93927054818871

\section{Recognize inefficiencies and suggest changes}

The report will filter all machines that reported non-optimal - negative distance from intersection point - configuration during measurement period (29 days).

Number of machines to tune: 932
CPU capacity to accommodate: 1 320 781.36
Memory capacity to accommodate: 4 286 742.06
Number of tasks to execute: 118869614
Cost of running non-optimal machines: \$657 200
Cost of heavy: \$29.56
Cost of medium: \$657 170.44
Total uptime: 648519
cost per hour = \$1.01338588383687
Cost per task =  \$657 200 / 118869614 = \$0.00552874681666

Avg cpu usage per machine = 15972217.38/12583 = 1269.35/29 = 43.77
Avg mem usage per machine = 30676363.36/12583 = 2437.92/29 = 84.06
Avg tasks number per machine = 1234716525/12583 = 98125.77/29 = 3383.65

\myparagraph{Squeeze-them-in suggestion strategy}

total spare cpu = 3 697 171.44
total spare mem = 6 685 407.83
total distance: +3 500 037
total uptime = 8056601
cost per hour = \$7 519 848 / 8056601 = 0.93337723935938
new total cost = \$8 177 048 - \$657 200 = \$7 519 848
new cost per task = \$7 519 848 / 1234716525 = 0.00609034369245

new averages 
cpu per machine = 15972217.38/11651 = 1370.88 / 29 = 47.27
Avg mem usage per machine = 30676363.36/11651 = 2632.94/29 = 90.79
Avg tasks number per machine = 1234716525/11651 = 105975.15/29 = 3654.31
